---
title: "mlr3 benchmarking"
output: html_notebook
---

This notebook runs benchmarks on three different datasets `GOQ`, `PI`, `GOPI` using the **mlr3** packages.

```{r}
#| label: load-packages
#| echo: false

library(ggplot2)
library(scales)

library(mlr3)
library(mlr3learners)
library(mlr3extralearners)
library(mlr3viz)
library(mlr3pipelines)
library(glue)
```

![mlr3 building blocks](ml_abstraction.svg){#fig-resample}

We first set the seed to allow reproducibility of the code.

```{r}
#| label: set-seed
set.seed(123)
```

We can set the different learner models:

```{r}
#| label: list-learners
learners = list(lrn("regr.featureless"),
                lrn("regr.lm"),
                lrn("regr.ranger"),
                lrn("regr.km", nugget.stability = 1e-8, covtype = "powexp"),
                lrn("regr.ksvm"),
                lrn("regr.rpart"))
```

Wrap each learner in a one-hot encoder for categorical features (gas)

```{r}
#| label: encode-categorical
learners = lapply(learners, function(l) po("encode") %>>% po("learner", l))
```

Load the data and remove meta-data columns

```{r}
#| label: create-tasks

setwd("..")
d.goq = subset(read.csv("GOQ.csv", stringsAsFactors = TRUE), select = -c(campaign, initial))
task.goq = TaskRegr$new(id = "GOQ", backend = d.goq, target = "target")

d.gopi = subset(read.csv("GOPI.csv", stringsAsFactors = TRUE), select = -c(campaign, initial))
task.gopi = TaskRegr$new(id = "GOPI", backend = d.gopi, target = "target")

d.pi = subset(read.csv("PI.csv", stringsAsFactors = TRUE), select = -c(campaign, initial))
task.pi = TaskRegr$new(id = "PI", backend = d.pi, target = "target")
```

Run each learner on each task, with a 10-fold CV

```{r}
#| label: benchmark-design
#| results: hide
#| warning: false

design = benchmark_grid(
    tasks = list(task.goq, task.pi, task.gopi),
    learners = learners,
    resamplings = rsmp("cv", folds = 10)
)
bmr = benchmark(design)
```
```{r}
#| label: scatterplot
p = autoplot(bmr, measure = msr("regr.mae")) +
    theme(text = element_text(size=15), axis.text.x = element_text(angle = 55, hjust = 1)) +
    expand_limits(y = 0)
p
```
